### 2020-04-27 draft_ABP.tex
Updates from Overleaf

The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
The stringy canonical form of this building set $\mathcal I_{\mathbf B}(\{S\})$
is related with the original string integral eq.\eqref{stringint} by 
\[
	z_{j}-z_i=x_{[i,j-1]},
\]
so Mandelstam variables are related to $S$ by $s_{ij}=S_{[i,j-1]}$.
The facets of $\mathscr A_n$ are given by
\[
	F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\begin{equation}\label{Ansf}
S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]},
\end{equation}
where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite 
the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
\begin{align*}
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
&=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}x_{[i,j]}^{F_{[i+1,j-1]}}\bigg /
x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}\\
&=
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}
\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}}
\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}}
\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
\end{align*}
and we get that
\[
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
\]
with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, whose $u$-equations are
\[
1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
\]

The ABHY construction of $\mathscr A_n$ is given by 
\[
	S_{[i,j]}=-c_{[i,j]} \,\,\text{ for all $i<j$,}\quad
	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
\]
where $c$s are positive numbers. We can use a mesh to represent these conditions.
For example, the mesh of $\mathscr A_3$ is 
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (-0.5,1) {$[0,2]$};
	\node at (1.35,1) {$[1,3]$};
	\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
Each diamond in the mesh whose top corner\footnote{
It looks different with the usual mesh where label of $c$ follows the left corner
in each diamond. This is because the mismatch of the correspondence of labels 
$F_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
}
is label by $[i,j]$ represents 
\[
	c_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
\]
and each big diamond (which is made of several diamonds) gives us an equation
\[
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$

@@

The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
The facets are given by 
\[
F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\[
	S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$ and $[i,j]\neq [0,n]$},
\]
and
\[
	S_{[0,n]}=F_{[0,n]}-\sum_{i=0}^n F_{[i,i-2]} +\sum_{i=0}^n F_{[i,i-3]},
\]
where $F_{[i+1,i]}=F_{[0,n]}=0$. Therefore, the $u$-variables are
\[
u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
\quad \text{for $i-j\neq 2$}.
\]
$u$-equations are
\[
1-u_i=U_{[i+1,i-1]},\quad 
1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
\]
where 
\[
U_{A,B}=\prod_{a\in A,b\in B}u_{ab},\quad 
U_A=\prod_{a\in A}u_a\prod_{a<b\in A}u_{ab}.
\]

The ABHY construction of $\mathscr B_n$ is similar: $F_{[i,j]}\geq 0$ for all $[i,j]\in\mathbf B$,
\[
	F_{[i,j-1]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}
	=c_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
\]
and 
\begin{equation}\label{abhyB}
	c_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
\end{equation}
where $F_{[i+1,i]}=0$ and $c$s are all positive constants. We can also
use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$
is 
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
	\draw[thick] (2,1) -- (4,-1) -- (5,-2);
	\draw[thick] (4,1) -- (6,-1);
	\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
	\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
	\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (5.35,-1) {$[0,0]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (4.35,0) {$[3,0]$};
	\node at (6.35,0) {$[0,1]$};
	\node at (0,1.2) {$[0,2]$};
	\node at (2,1.2) {$[1,3]$};
	\node at (4,1.2) {$[2,0]$};
	\node at (6,1.2) {$[3,1]$};
\end{tikzpicture}
\end{center}
with an additional equation \eqref{abhyB}.

@@

The degenerations of $A_n$ is given by setting some $c$s in ABHY construction or deleting the corresponding elements in the building set. Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $A_n$ may not be a generalized permutohedron. However, we can still ask the following question: are these degenerations binary geometries? 
Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set minus one, \emph{i.e.} its big polytope is a simplex.
Before answer this question, let's first find all degenerations of $A_n$ with this property.

@@

From the following equations for facets $\{F_{[i,j]}\}$ of $A_n$
\[
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}=
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} 
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} c_{[a,b]} 
\quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
\text{or}&\\
&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} c_{[a,b]} 
\quad \text{for $0<j\leq n$ and $0\leq k<n$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
	-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
\end{tikzpicture}
\qquad \text{or}\qquad
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\end{tikzpicture}
\end{center}
we can see that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation forces $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
\draw[thick] (-1,-2) -- (2,1);
\draw[thick] (-2,-1) -- (-1,-2);
\draw[thick] (-1,0) -- (1,-2) -- (3,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
\node at (-2.5,-1) {$[0,0]$};
\node at (-0.65,-1) {$[1,1]$};
\node at (1.35,-1) {$[2,2]$};
\node at (3.35,-1) {$[3,3]$};
\node at (-1.5,0) {$[0,1]$};
\node at (0.35,0) {$[1,2]$};
\node at (2.35,0) {$[2,3]$};
\node at (-0.5,1) {$[0,2]$};
\node at (1.35,1) {$[1,3]$};
\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
	\{[0,3],[0,2],[0,1],[0,0],[1,1],[2,2],[3,3]\}.
\]
One can further check that it's a cube (or $A_1^3$).

We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices. For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.

@@

Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
  \bea
{\mathscr P_n}^y(\{y_I \})= \sum y_I . \Delta_I  
 \eea
 for some collection of subsets $I \in [0,n]$
 We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums i.e., all $y_I \ge 0$ \footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.}which are called Nestohedra. Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\

@@

\subsubsection*{Nested Complex}
A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item ${\mathbf N}$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\

 {\bf Facial structure:}

 Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$. Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.

@@

In summary the above results mean the following:\\

(1) We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set. \\

(2) The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set. \\

(3) Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.

Let us look at a couple of examples to appreciate these facts better:\\
(1) Consider the generalized permutahedron with building set ${\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}$.

The polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below.

>>>>

The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
The stringy canonical form of this building set $\mathcal I_{\mathbf B}(\{S\})$
is related with the original string integral eq.\eqref{stringint} by 
\[
	z_{j}-z_i=x_{[i,j-1]},
\]
so Mandelstam variables are related to $S$ by $s_{ij}=S_{[i,j-1]}$.
The facets of $\mathscr A_n$ are given by
\[
	F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\begin{equation}\label{Ansf}
S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]},
\end{equation}
where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$.
The usual $X$-variable $X_{ij}=\sum_{i\leq k<l<j}s_{kl}$ in string integrals here is $F_{[i,j-2]}$. 
Using this solution to rewrite 
the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
\begin{align*}
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
&=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}x_{[i,j]}^{F_{[i+1,j-1]}}\bigg /
x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}\\
&=
\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}
\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}}
\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}}
\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
\end{align*}
and we get that
\[
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
\]
with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, whose $u$-equations are
\[
1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
\]

The ABHY construction of $\mathscr A_n$ is given by 
\[
	S_{[i,j]}=-C_{[i,j]} \,\,\text{ for all $i<j$,}\quad
	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
\]
where $C$s are positive numbers. We can use a mesh to represent these conditions.
For example, the mesh of $\mathscr A_3$ is 
\begin{center}
\begin{tikzpicture}
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
	\node at (-2.5,-1) {$[0,0]$};
	\node at (-0.65,-1) {$[1,1]$};
	\node at (1.35,-1) {$[2,2]$};
	\node at (3.35,-1) {$[3,3]$};
	\node at (-1.5,0) {$[0,1]$};
	\node at (0.35,0) {$[1,2]$};
	\node at (2.35,0) {$[2,3]$};
	\node at (-0.5,1) {$[0,2]$};
	\node at (1.35,1) {$[1,3]$};
	\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
Each diamond in the mesh whose top corner\footnote{
It looks different with the usual mesh where label of $c$ follows the left corner
in each diamond. This is because the mismatch of the correspondence of labels 
$X_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
}
is label by $[i,j]$ represents 
\[
	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
\]
and each big diamond (which is made of several diamonds) gives us an equation
\[
	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$

@@

The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
The facets are given by 
\[
F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
\]
and their solution is 
\[
	S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$ and $[i,j]\neq [0,n]$},
\]
and
\[
	S_{[0,n]}=F_{[0,n]}-\sum_{i=0}^n F_{[i,i-2]} +\sum_{i=0}^n F_{[i,i-3]},
\]
where $F_{[i+1,i]}=F_{[0,n]}=0$. Therefore, the $u$-variables are
\[
u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
\quad \text{for $i-j\neq 2$}.
\]
$u$-equations are
\[
1-u_i=U_{[i+1,i-1]},\quad 
1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
\]
where 
\[
U_{A,B}=\prod_{a\in A,b\in B}u_{ab},\quad 
U_A=\prod_{a\in A}u_a\prod_{a<b\in A}u_{ab}.
\]
Since the building set of $\mathscr A_n$ is contained in the building set of $\mathscr B_n$, $\mathscr A_n$ is a degeneration of $\mathscr B_n$.

The ABHY construction of $\mathscr B_n$ is similar: $F_{[i,j]}\geq 0$ for all $[i,j]\in\mathbf B$,
\[
	F_{[i,j-1]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}
	=C_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
\]
and 
\begin{equation}\label{abhyB}
	C_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
\end{equation}
where $F_{[i+1,i]}=0$ and $C$s are all positive constants. 
%We can also use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$ is 
%\begin{center}
%\begin{tikzpicture}
%	\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
%	\draw[thick] (-2,-1) -- (-1,-2);
%	\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
%	\draw[thick] (2,1) -- (4,-1) -- (5,-2);
%	\draw[thick] (4,1) -- (6,-1);
%	\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
%	\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
%	\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
%	\node at (-2.5,-1) {$[0,0]$};
%	\node at (-0.65,-1) {$[1,1]$};
%	\node at (1.35,-1) {$[2,2]$};
%	\node at (3.35,-1) {$[3,3]$};
%	\node at (5.35,-1) {$[0,0]$};
%	\node at (-1.5,0) {$[0,1]$};
%	\node at (0.35,0) {$[1,2]$};
%	\node at (2.35,0) {$[2,3]$};
%	\node at (4.35,0) {$[3,0]$};
%	\node at (6.35,0) {$[0,1]$};
%	\node at (0,1.2) {$[0,2]$};
%	\node at (2,1.2) {$[1,3]$};
%	\node at (4,1.2) {$[2,0]$};
%	\node at (6,1.2) {$[3,1]$};
%\end{tikzpicture}
%\end{center}
%with an additional equation \eqref{abhyB}.

@@

The degenerations of $A_n$ is given by setting some $C$s in ABHY construction or deleting the corresponding elements in the building set. Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $A_n$ may not be a generalized permutohedron. However, we can still ask the following question: are these degenerations binary geometries? 
Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set minus one, \emph{i.e.} its big polytope is a simplex.
Before answer this question, let's first find all degenerations of $A_n$ with this property.

@@

From the following equations for facets $\{F_{[i,j]}\}$ of $A_n$
\[
	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}=
	\sum_{i\leq a<j\atop{k<b\leq l}} C_{[a,b]} 
\]
where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
an economical way to get a degeneration which satisfies the above property is setting all $C$s on the RHS of 
\begin{align*}
&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} C_{[a,b]} 
\quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
\text{or}&\\
&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} C_{[a,b]} 
\quad \text{for $0<j\leq n$ and $0\leq k<n$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $C$s in several above equations.

From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $C$s are zero. For example,
\begin{center}
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
	-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
\end{tikzpicture}
\qquad \text{or}\qquad
\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
\draw (-1,-1) -- (1,1);
\draw (-1,1) -- (2,-2);
\draw (0,-2) -- (2,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
\end{tikzpicture}
\end{center}
we can see that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation forces $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $C$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
\draw[thick] (-1,-2) -- (2,1);
\draw[thick] (-2,-1) -- (-1,-2);
\draw[thick] (-1,0) -- (1,-2) -- (3,0);
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
\node at (-2.5,-1) {$[0,0]$};
\node at (-0.65,-1) {$[1,1]$};
\node at (1.35,-1) {$[2,2]$};
\node at (3.35,-1) {$[3,3]$};
\node at (-1.5,0) {$[0,1]$};
\node at (0.35,0) {$[1,2]$};
\node at (2.35,0) {$[2,3]$};
\node at (-0.5,1) {$[0,2]$};
\node at (1.35,1) {$[1,3]$};
\node at (1,2.2) {$[0,3]$};
\end{tikzpicture}
\end{center}
after setting $C$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
	\{[0,3],[0,2],[0,1],[0,0],[1,1],[2,2],[3,3]\}.
\]
One can further check that it's a cube (or $A_1^3$).

We can play the game for any degenerations of $A_n$, count black points and deleted $C$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices. For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.

@@

Let $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
\bea
{\mathscr P_n}^y(\{y_I \})= \sum y_I . \Delta_I  
\eea
for some collection of subsets $I \in [0,n]$.
We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums i.e., all $y_I \ge 0$ \footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.}which are called Nestohedra. Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\

@@

\paragraph*{Nested Complex} 
A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item ${\mathbf N}$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\

\paragraph*{Facial structure} 
Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$. Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.

@@

In summary the above results mean the following:

\begin{compactitem}
\item We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set.

\item The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set.

\item Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.
\end{compactitem}

Let us look at a couple of examples to appreciate these facts better:

(1) Consider the generalized permutahedron with building set 
\[{\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}.\]
The polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below.

The polytope in this case is the 2d associahedron ${\mathscr A_2}$.
